---
title: "IntroductionRppsc"
author: "Jiayan Wang"
date:  "`r format(Sys.time(), '%d %b %Y')`"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{IntroductionRppsc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Rppsc)
```

## Introduction

**Rppsc** is a R package for plotting protein sequence composition. The package benefits from the *protr* package and its determination on the chemical proterty of amino acid.

To start, the lattest version of *Rppsc* package can be installed via github 
```{r eval=FALSE, include=TRUE}
require("devtools")
install_github("dxjasmine/Rppsc", build_vignettes = TRUE)
library(Rppsc)
```


## Plotting sequence composition for multiple proteins. 
*Rppsc* provide visualization of protein sequence composition with regard to 5 aspects. They are hydrophobiciy, van der Waals volume, polarity
polarizability, and desolvation. The 5 attributes are frequently used evaluate the surface and structure property. This distribution of each attributes is useful in assessment of protein sequence including domain, structure, and function analysis. 


```{r fig.width=7,fig.height=6}
#user can use their own csv file providing pdbid and seuquence
#Default data --"proSeq" are also provided
hydrophobicity_plot <- plotCG(file = "proSeq", type= 1, circular_plot = TRUE)
hydrophobicity_plot #call to view the plot
```

## Plotting sequence composition with 5 chemical attributes.


```

## Rppsc shiny app
`Rppsc` can also be accessed as a shiny ap to interactively view the features mentioned above. The app aims to show the visualization of the protein sequence composition with regard to 5 attributes. 



## Reference
Xiao, N., Cao, D.-S., Zhu, M.-F., & Xu, Q.-S. (2015). protr/ProtrWeb: R package and web server for generating various numerical representation schemes of protein sequences. Bioinformatics, 31(11), 1857–1859. https://doi.org/10.1093/bioinformatics/btv042
